---
title: "PSTAT131_HW3"
author: "Luke Todd"
date: "4/18/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(here)
library(ggplot2)
library(tidyverse)
library(tidymodels)
library(corrr)
library(corrplot)
library(ggthemes)
library(yardstick)
library(discrim)
library(poissonreg)
library(klaR)
tidymodels_prefer()

titanic <- read_csv(here("hw 3/data/titanic.csv"))

set.seed(3068)

```

#### Changing survived and pclass to factors
```{r}

titanic$survived <- factor(titanic$survived, levels = c("Yes", "No"))
levels(titanic$survived)

titanic$pclass <- factor(titanic$pclass)
class(titanic$pclass)

# titanic <- read_csv(file = "data/titanic.csv") %>% 
#   mutate(survived = factor(survived, 
#                            levels = c("Yes", "No")),
#          pclass = factor(pclass))

```


### Question 1
```{r}

titanic_split <- initial_split(titanic, prop = 0.8,
                               strata = survived)

titanic_train <- training(titanic_split)
titanic_test <- testing(titanic_split)

dim(titanic_train)

```

I think that using stratified sampling is good for this data because we won't get a skewed random sample. It better represents the entire population.


### Question 2
```{r}

# plot(titanic_train$survived)

titanic_train %>%
  ggplot(aes(x = survived)) + 
  geom_bar()

```
The survived variable's distribution shows that it was more common for someone on the Titanic to die, than it was for them to survive.

### Question 3
```{r}

cor_titanic <- titanic_train %>%
  select(-survived, -pclass, -name, -sex, -ticket, -cabin, -embarked) %>%
  correlate()

rplot(cor_titanic)

cor_titanic %>%
  stretch() %>%
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))))

```
The highest levels of correlation are between sib_sp and age, with a negative correlation of 0.31, as well as sib_sp and parch, with a positive correlation of 0.43. These correlation levels are not very high.


### Question 4
```{r}

titanic_recipe <- recipe(survived ~ pclass, sex, age, sib_sp, parch, fare, data = titanic_train) %>%
  step_impute_linear() %>%
  step_interact(terms = ~ sex:fare +
                  age:fare) %>%
  step_dummy(all_nominal_predictors())

```


### Question 5
```{r}

log_reg <- logistic_reg() %>%
  set_engine("glm") %>%
  set_mode("classification")

log_wkflow <- workflow() %>%
  add_model(log_reg) %>%
  add_recipe(titanic_recipe)

log_fit <- fit(log_wkflow, titanic_train)

log_fit %>% tidy()

```


### Question 6
```{r}

lda_mod <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

lda_wkflow <- workflow() %>% 
  add_model(lda_mod) %>% 
  add_recipe(titanic_recipe)

lda_fit <- fit(lda_wkflow, titanic_train)

```


### Question 7
```{r}

qda_mod <- discrim_quad() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

qda_wkflow <- workflow() %>% 
  add_model(qda_mod) %>% 
  add_recipe(titanic_recipe)

qda_fit <- fit(qda_wkflow, titanic_train)

```


### Question 8
```{r}

nb_mod <- naive_Bayes() %>% 
  set_mode("classification") %>% 
  set_engine("klaR") %>% 
  set_args(usekernel = FALSE) 

nb_wkflow <- workflow() %>% 
  add_model(nb_mod) %>% 
  add_recipe(titanic_recipe)

nb_fit <- fit(nb_wkflow, titanic_train)

```


### Question 9
```{r}

predict(log_fit, new_data = titanic_train, type = "prob")
log_reg_acc <- augment(log_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
log_reg_acc

predict(lda_fit, new_data = titanic_train, type = "prob")
lda_acc <- augment(lda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
lda_acc

predict(qda_fit, new_data = titanic_train, type = "prob")
qda_acc <- augment(qda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
qda_acc

predict(nb_fit, new_data = titanic_train, type = "prob")
nb_acc <- augment(nb_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
nb_acc

```

Log fit and LDA fit had the highest accuracy on the training data.


### Question 10
```{r}

predict(log_fit, new_data = titanic_test, type = "prob")

# confusion matrix
augment(log_fit, new_data = titanic_test) %>%
  conf_mat(truth = survived, estimate = .pred_class) 

augment(log_fit, new_data = titanic_test) %>%
  accuracy(truth = survived, estimate = .pred_class)

```














